---
title: "Plotly"
output: 
  html_document:
    toc: true
    toc_float: true
---

## Load data

```{r message=FALSE}
library(tidyverse)
library(plotly)
library(p8105.datasets)
```

Let's get a small dataset of Airbnb's in NYC:

```{r}
data("nyc_airbnb")

nyc_airbnb =
  nyc_airbnb |>
  mutate(stars = review_scores_location / 2) |>
  select(borough = neighbourhood_group,
         neighbourhood, stars, price, room_type, lat, long) |>
  drop_na(stars) |>
  filter(
    borough == "Manhattan",
    room_type == "Entire home/apt",
    price %in% 100:500)
```

## Interactive scatterplot

We can add the price and rating/stars by creating a string `text_label` and it will show up when you hover over the item.

* backslash-n in the code means a line break

```{r}
nyc_airbnb |>
  mutate(text_label = str_c("Price: $", price, "\nRating: ", stars)) |>
  plot_ly(x = ~lat, y = ~long, color = ~price, text = ~text_label,
          type = "scatter", mode = "markers", alpha = 0.8)
```

## Interactive boxplot

```{r warning=FALSE}
nyc_airbnb |> 
  mutate(neighbourhood = fct_reorder(neighbourhood, price)) |> 
  plot_ly(y = ~price, color = ~neighbourhood, type = "box", colors = "viridis")
```

## Interactive bar plot

```{r warning=FALSE}
nyc_airbnb |>
  count(neighbourhood) |>
  mutate(neighbourhood = fct_reorder(neighbourhood, n)) |>
  plot_ly(x = ~neighbourhood, y = ~n, color = ~neighbourhood, type = "bar", colors = "viridis")
```

## ggplotly

This exists, but Prof. Goldsmith doesn't recommend using it. The quality of the graphic is not as good and the interactivity is slower.

```{r}
ggp_scatter =
  nyc_airbnb |>
  ggplot(aes(x = lat, y = long, color = price)) +
  geom_point(alpha = 0.5)

ggplotly(ggp_scatter)
```

## Dashboard

You can start with a template or File --> New File --> R Markdown --> From Template --> Flex Dashboard.

My code for the dashboard is in my local dashboard.Rmd file.